---
title: "Standard Single Cell RNA Seq Analysis"
author: "Wesley Blashka"
date: "`r Sys.Date()`"
output: 
  tufte::tufte_html
knit: |
  (function(input,...){
    rmarkdown::render(
      input,
      output_file = paste0(
      xfun::sans_ext(input),'-',Sys.Date(),'.'
      ),
      envir = globalenv()
    )
  })
---
<script src="code-folding.js"></script>

# Setup

Functions pulled from `https://raw.githubusercontent.com/UW-Brown-Lab/scRNAseq/main/scRNAseq_functions.R`
```{r Setup Env, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, collapse=TRUE, results = 'hold')

# Desc: Loads all necessary packages cached in compiled CTHC transferred  file

library(jsonlite)
library(tidyverse)
library(DropletUtils)
library(Seurat)
library(ShinyCell)
library(Matrix)
library(scales)
library(rjson)
library(R2HTML)
library(SingleCellExperiment)
library(scDblFinder)
library(SoupX)
library(patchwork)
library(glmGamPoi)
library(scRepertoire)
library(tufte)

# Load modular functions
source('https://raw.githubusercontent.com/UW-Brown-Lab/scRNAseq/main/scRNAseq_functions.R')
```

## Load Paramaters from JSON
Load in the parameters for all downstream processing from `r-analysis-params.json`. These will dictate the settings for all of the following functions.
```{r Load Parameters, class.source= 'fold-hide'}
# Parse the JSON file and load the params
config <- jsonlite::fromJSON("r-analysis-params.json")
file.copy("r-analysis-params.json", paste0(config$analysis_title, " - parameters.json"))
```

# Import Count Data

Load 10X formatted data for each sample specified in the parameters using the `file_path`. Samples must be in the h5 file format. Store these in a list of items named by sample names, each containing the raw and filtered counts.

```{r Import Count Data, class.source= 'fold-hide'}
loaded_counts <- ImportCountData(config$samples, config$directory_info)
```

# Estimate cell free mRNA Contamination

Use SoupX to estimate cell free mRNA Contamination. Create a SoupChannel object using the imported data, perform clustering of the filtered data before SoupX filtering to identify clusters to pass to SoupX, estimate contamination, and de-contaminate each sample.

```{r Estimate Contamination with SoupX, warning=FALSE, class.source= 'fold-hide'}
cleaned_counts <- DecontaminateSoup(loaded_counts, config$dimensional_reduction_settings)

# Remove and GC to conserve memory
rm(loaded_counts)
gc()
```

# Identify and remove Doublets

Use scDblFinder to identify potential doublets. This compares artificially concatenated doublets with potential doublets. Remove identified doublets from the experiment

```{r Remove Doublets, class.source= 'fold-hide'}
set.seed(1337)
sce_and_before_plot <- GenerateSCEobjects(cleaned_counts, config)
filtered_sce_list <- RemoveDoublets(sce_and_before_plot$sce_list)
merge_and_after_plot <- CreateMergedSeurat(filtered_sce_list, config)

# Show QC plots
sce_and_before_plot$before_plot
merge_and_after_plot$after_plot

# Remove and GC to conserve memory
rm(sce_and_before_plot)
rm(cleaned_counts)
rm(filtered_sce_list)
gc()
```

# Subsequent Filtering  (%MT, nCount_RNA, nFeature_RNA)

Determine the percent of the features that come from mitochondrial RNA. Then subset the merged Seurat object to only include cells within acceptable limits as defined in the configuration file.

```{r Filtering of Seurat, class.source= 'fold-hide'}
subsetted_seurat_and_plots <- FilterSeuratObject(merge_and_after_plot$seurat, config)

# Show QC plots
for (i in seq_along(subsetted_seurat_and_plots)){
  sample <- subsetted_seurat_and_plots[[i]]
  print(sample[["plot_b"]])
  print(sample[["plot_a"]])
}

# Remove and GC to conserve memory
rm(merge_and_after_plot)
gc()
```
# Clustering and Feature Identification

Perform Clustering and Dimensional Reduction. Normalize/scale with SCTransform. Generate feature plots from config.

```{r Cluster Analysis, warning=FALSE, class.source= 'fold-hide'}
# Cluster Analysis
clustered_seurat_and_plots <- ClusterAnalysis(subsetted_seurat_and_plots,config)
print(clustered_seurat_and_plots$plots)
saveRDS(clustered_seurat_and_plots$seu,paste0(config$analysis_title, "_seu.RDS"))
gc()
```



### Parameters
```{r Print Parameters, class.source= 'fold-hide'}
print(config)
```



### Session Info
```{r Print Session Info, class.source= 'fold-hide'}
print(sessionInfo())

```

