---
title: "scRNAseq Analysis"
author: "Wesley Blashka"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: bootstrap
params:
  params_path:"./r-analysis-params.json"
---

```{r Setup Env, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE)

# Desc: Loads all necessary packages cached in compiled CTHC transferred  file

library(jsonlite)
library(tidyverse)
library(DropletUtils)
library(Seurat)
library(ShinyCell)
library(Matrix)
library(scales)
library(rjson)
library(R2HTML)
library(SingleCellExperiment)
library(scDblFinder)
library(SoupX)

# Load modular functions
source('functions.R')
```

## Load Paramaters from JSON
Load in the parameters for all downstream processing from `r-analysis-params.json`. These will dictate the settings for all of the following functions.
```{r Load Parameters}
# Parse the JSON file and load the params
config <- jsonlite::fromJSON("r-analysis-params.json")
```

## Import Count Data

Load 10X formatted data for each sample specified in the parameters using the `file_path`. Samples must have a matrix.mtx, features.tsv, and barcodes.tsv. Store these in a list of items named by sample names, each containing the raw and filtered counts.

```{r Import Count Data}
loaded_counts <- ImportCountData(config$samples, config$directory_info)
```

## Estimate cell free mRNA Contamination

Use SoupX to estimate cell free mRNA Contamination. Create a SoupChannel object using the imported data, perform clustering of the filtered data before SoupX filtering to identify clusters to pass to SoupX, estimate contamination, and de-contaminate each sample.

```{r Estimate Contamination with SoupX, warning = FALSE}
cleaned_counts <- DecontaminateSoup(loaded_counts, config$dimensional_reduction_settings)
# Remove and GC to conserve memory
rm(loaded_counts)
gc()
```

## Identify and remove Doublets

Use scDblFinder to identify potential doublets. This compares artificially concatenated doublets with potential doublets. Remove identified doublets from the experiment

```{r Remove Doublets}
set.seed(1337)
sce_and_before_plot <- GenerateSCEobjects(cleaned_counts)
filtered_sce_list <- RemoveDoublets(sce_and_before_plot$sce_list)
merge_and_after_plot <- CreateMergedSeurat(filtered_sce_list)

# Show QC plots
sce_and_before_plot$before_plot
merge_and_after_plot$after_plot

# Remove and GC to conserve memory
rm(sce_and_before_plot)
rm(filtered_sce_list)
gc()
```

## Subsequent Filtering  (%MT, nCount_RNA, nFeature_RNA)

Determine the percent of the features that come from mitochondrial RNA. Then subset the merged Seurat object to only include cells within acceptable limits as defined in the configuration file.

```{r}
subsetted_seurat_and_plots <- FilterSeuratObject(merge_and_after_plot$seurat, config$filter_options$thresholds)

# Show QC plots
subsetted_seurat_and_plots$plot_b
subsetted_seurat_and_plots$plot_a

# Remove and GC to conserve memory
rm(merge_and_after_plot)
gc()
```

